Carrier phase and amplitude estimation using pilots and data

### 2012-05-06 paper.tex
Added to paper.

\begin{theorem}
Let $\{w_i\}$ be a sequence independent and identically distributed, zero mean, circularly symetric complex random variables and let $\{\Phi_i\}$ be the sequence of idenpendent and identically distributed random variables given by $\Phi_i = \angle{(\rho_0 + w_i)}$.  Put 
\[
h_1 = \prob e^{j\round{\Phi_1}} \qquad \text{and} \qquad h_2 = \prob w_1 e^{j\round{\Phi_1}}.
\]
Given the observed noisy data symbols $\{y_i, i \in P \cup D\}$ from~\eqref{eq:sigmod} let $\hat{a}$ be the least squares estimator of $a_0$.  Let $\hat{a} = \hat{\rho}e^{j\hat{\theta}$ and $a_0 = \rho_0 e^{j\theta_0}$.  Put $L = \abs{P \cup D}$.  If 
\[
\frac{\abs{P}}{L} \rightarrow p \qquad \text{and} \qquad \frac{\abs{D}}{L} \rightarrow d
\] 
as $L \rightarrow \infty$ for positive real numbers $p$ and $d$, and if both $h_1$ and $h_2$ are positive real numbers, then:
\begin{enumerate}
\item $\sfracpart{\theta_0 - \hat{\theta}} \rightarrow 0$ almost surely as $L \rightarrow \infty$,
\item $\hat{\rho} \rightarrow \rho_0( p + d h_1 ) + h_2$ almost surely as $L \rightarrow \infty$,
\item Put $\lambda_L = \sfracpart{\theta_0 - \hat{\theta}}$ and $m_L = \hat{\rho} - \rho_0( p + d h_1 ) + h_2$.  Then the vector $[\lambda_L, m_L]$ converges to the bivariate normal distribution with zero mean and covariance
\[
C = ?
\]
as $L \rightarrow \infty$.
\end{enumerate}
\end{theorem}

@@

We now prove the asymptotic normality of the estimator.  At the same time we are able to describe the distribution of the magnitude estimator $\hat{\rho}$.  Observe that $Z(\theta) = e^{-j\theta}Y(\{\hat{d}_i(\hat{\theta}), i \in D\})$.  From~\eqref{eq:ahatYhat} we obtain
\begin{align*}\label{eq:hata}
\hat{a} e^{-j\theta} &= \hat{\rho} e^{j(\hat{\theta} - \theta)} = \hat{\rho} e^{j\lambda_L} \\
&= \frac{1}{L} e^{-j\theta} Y(\{\hat{d}_i(\hat{\theta}), i \in D\}) \\
&= \frac{1}{L}  Z(\hat{\theta}) \\
&= \frac{1}{L} \sum_{i \in P} \rho_i e^{j(\lambda_L + \Phi_i)} + \frac{1}{L}  \sum_{i \in D}  \rho_i e^{j( \lambda_L + \Phi_i - \round{\lambda_L + \Phi_i})}
\end{align*}
and muliplying both sides of this equation by $e^{-j\lambda_L}$,
\begin{align*}\label{eq:hatrhoworking}
\hat{\rho} &=  \frac{1}{L} \sum_{i \in P} \rho_i e^{j\Phi_i} + \frac{1}{L}  \sum_{i \in D}  \rho_i e^{j(\Phi_i - \round{\lambda_L + \Phi_i})} \\
 &=  \frac{1}{L} \sum_{i \in P} (\rho_0 + w_i) + \frac{1}{L}  \sum_{i \in D}  (\rho_0 + w_i)e^{-j\round{\lambda_L + \Phi_i}} 
\end{align*}

>>>>

\begin{theorem}
Let $\{w_i\}$ be a sequence independent and identically distributed, zero mean, circularly symetric complex random variables and let $\{\Phi_i\}$ be the sequence of idenpendent and identically distributed random variables given by $\Phi_i = \angle{(\rho_0 + w_i)}$.  Put 
\[
h_1 = \prob e^{-j\round{\Phi_1}} \qquad \text{and} \qquad h_2 = \prob w_1 e^{-j\round{\Phi_1}}.
\]
Given the observed noisy data symbols $\{y_i, i \in P \cup D\}$ from~\eqref{eq:sigmod} let $\hat{a}$ be the least squares estimator of $a_0$.  Let $\hat{a} = \hat{\rho}e^{j\hat{\theta}$ and $a_0 = \rho_0 e^{j\theta_0}$.  Put $L = \abs{P \cup D}$.  If 
\[
\frac{\abs{P}}{L} \rightarrow p \qquad \text{and} \qquad \frac{\abs{D}}{L} \rightarrow d
\] 
as $L \rightarrow \infty$ for positive real numbers $p$ and $d$, and if both $h_1$ and $h_2$ are positive real numbers, then:
\begin{enumerate}
\item $\sfracpart{\theta_0 - \hat{\theta}} \rightarrow 0$ almost surely as $L \rightarrow \infty$,
\item $\hat{\rho} \rightarrow \rho_0( p + d h_1 ) + h_2$ almost surely as $L \rightarrow \infty$,
\item Put $\lambda_L = \sfracpart{\theta_0 - \hat{\theta}}$ and $m_L = \hat{\rho} - \rho_0( p + d h_1 ) + h_2$.  Then the vector $[\sqrt{N}\lambda_L, \sqrt{N}m_L]$ converges to the bivariate normal distribution with zero mean and covariance
\[
C = ?
\]
as $L \rightarrow \infty$.
\end{enumerate}
\end{theorem}

@@

We now prove the asymptotic normality of the estimator.  At the same time we are able to describe the distribution of the magnitude estimator $\hat{\rho}$.  Observe that $Z(\theta) = e^{-j\theta}Y(\{\hat{d}_i(\hat{\theta}), i \in D\})$.  From~\eqref{eq:ahatYhat} we obtain
\begin{align}\label{eq:hata}
\hat{a} e^{-j\theta} &= \hat{\rho} e^{j(\hat{\theta} - \theta)} = \hat{\rho} e^{j\lambda_L} \nonumber \\
&= \frac{1}{L} e^{-j\theta} Y(\{\hat{d}_i(\hat{\theta}), i \in D\}) \nonumber \\
&= \frac{1}{L}  Z(\hat{\theta}) \nonumber \\
&= \frac{1}{L} \sum_{i \in P} \rho_i e^{j(\lambda_L + \Phi_i)} + \frac{1}{L}  \sum_{i \in D}  \rho_i e^{j( \lambda_L + \Phi_i - \round{\lambda_L + \Phi_i})} \label{eq:ahatfornorm}
\end{align}
and muliplying both sides of this equation by $e^{-j\lambda_L}$,
\begin{align*}\label{eq:hatrhoworking}
\hat{\rho} &=  \frac{1}{L} \sum_{i \in P} \rho_i e^{j\Phi_i} + \frac{1}{L}  \sum_{i \in D}  \rho_i e^{j(\Phi_i - \round{\lambda_L + \Phi_i})} \\
 &=  \frac{1}{L} \sum_{i \in P} (\rho_0 + w_i) + \frac{1}{L}  \sum_{i \in D}  (\rho_0 + w_i)e^{-j\round{\lambda_L + \Phi_i}}.
\end{align*}
By the strong law of large numbers, and since $\lambda_L \rightarrow 0$ (BLERG needs more care than this, but it's true),
\begin{align*}
\frac{1}{L}\sum_{i \in P}w_i \rightarrow 0 \\
\frac{1}{L}\sum_{i \in D}\rho_0e^{-j\round{\lambda_L + \Phi_i}} \rightarrow  \rho_0 h_1 \\
\frac{1}{L}\sum_{i \in P}w_i e^{-j\round{\lambda_L + \Phi_i}} \rightarrow h_2 \\
\end{align*}
and it immediately follows that $\hat{\rho} \rightarrow \rho_0( p + d h_1 ) + h_2$.  This proves statement 2 of our theorem.

We have
\begin{align*}
\sqrt{L} m_L =  A_L + B_L +  C_L
\end{align*}
where
\[
A_L = \frac{1}{\sqrt{L}} \sum_{i \in P}w_i,
\]
and
\[
B_L = \frac{\rho_0}{\sqrt{L}} \sum_{i \in D}(e^{-j\round{\lambda_L + \Phi_i}} - h_1),
\]
and
\[
C_L = \frac{1}{\sqrt{L}} \sum_{i \in D}(w_i e^{-j\round{\lambda_L + \Phi_i}} - h_2).
\]
Now $A_L$ converges in distribution to the complex normal with zero mean and variance $p\sigma^2$.
